### 2019-06-06 2-Chapters/Conclusion/conclusion.tex
Typos
Changed \paragraph{XXX} to \paragraph{XXX.}
Done for proofreading tonight
Added leftbar like in my Master thesis
Added https://arxiv.org/abs/1811.11043

% First chapter begins here
\chapter{General Conclusion and Perspectives}
% \addcontentsline{toc}{chapter}{General Conclusion}
\label{chapter:conclusion}
\minitoc

@@

% \newpage
\paragraph{Abstract}

This last chapter concludes the thesis, first by summarizing the previous chapters, and by giving a general conclusion of the thesis.
%
We highlight what we consider to be the most important directions of future works, as well as some promising directions that were shortly studied during my PhD but not discussed in the manuscript.

@@

% % ----------------------------------------------------------------------------
% \paragraph{Conclusion about \textbf{Chapter \ref{chapter:1}}}

% ----------------------------------------------------------------------------
\paragraph{Conclusion about \textbf{Chapter \ref{chapter:2}}}

@@

The first contribution of this manuscript \cite{Besson2018WCNC} concluded this chapter, in Section~\ref{sec:2:chooseYourPreferredBanditAlgorithm}. We tackle the question of how to select a particular bandit algorithm when a practitioner is facing a particular (unknown) bandit problem.
Instead of always choosing a fixed algorithm, or running costly benchmarks before real-world deployment of the chosen algorithm, we advise to select a few candidate algorithms, where at least one is expected to be very efficient for the given problem, and use online algorithm selection to automatically and dynamically decide the best candidate.
We proposed an extension of the Exp4 algorithm for this problem, \Aggr, and illustrate its performance on some bandit problems.

% ----------------------------------------------------------------------------
\paragraph{Conclusion about \textbf{Chapter \ref{chapter:3}}}

@@

We detailed how SMPyBandits is implementing arms, problems, algorithms, and use these components to implement a simulation loop, with various visualizations being performed after the simulation.
As far as now, SMPyBandits is restricted to the finite-arm cases, but it supports a wide range of arms distributions.
Different kinds of models are implemented, from stationary single-player to piece-wise stationary multi-player with different collision models.
One of the main quality of the library is that it is quite exhaustive, as all the main families of algorithms covering these different models have been implemented, even very recent algorithms from the literature, as we tried our best in following the active research since December $2016$ to June $2019$.
More than $65$ algorithms or variants of algorithms are implemented for the single-player case, $5$ for the expert aggregation problem, about $15$ for the multi-player case, and about $20$ for the piece-wise stationary problem.
All the codebase is fully documented, and the library is using continuous integration to run automated tests on the code after every modification.
%
When comparing algorithms on a problem, the main performance measure is the regret, but the library also computes, stores and visualizes other measures, such as best-arm selection rate or mean cumulated reward, as well as real time and memory costs.
%
Our library is used to run numerical simulations on Chapters~\ref{chapter:2}, \ref{chapter:5} and \ref{chapter:6}, and in other contributions such as our article \cite{Besson2018DoublingTricks}.

% ----------------------------------------------------------------------------
\paragraph{Conclusion about \textbf{Chapter \ref{chapter:4}}}

@@

% ----------------------------------------------------------------------------
\paragraph{Conclusion about \textbf{Chapter \ref{chapter:5}}}

The second chapter of Part~\ref{part:MABIOT} of this manuscript focussed on Multi-Player Multi-Arm Bandits models.
%
We present three variants of this model,
with different level of feedback being available to the decentralized players, under which we proposed efficient algorithms.
For the two easiest models --with sensing--, our theoretical contribution improves both the state-of-the-art upper and lower bounds on the regret. In the absence of sensing, we also provide some motivation for the practical use of the interesting \Selfish{} heuristic, a simple index policy based on hybrid indices that are directly taking  into account the collision information.
%
We also reviewed various variants of this model, and for some interesting variants we discussed the related literature, which has proved to be very active in the last two years. For some models, we explained why our approach does not work efficiently without modifications, but we detailed and illustrated how to adapt \MCTopM{} to other settings.
For example, it assumes to know the number of players $M$ before-hand, but we illustrated that previously introduced technique to estimate $M$ can also be applied to our proposal and give satisfactory empirical performances.
% Further works would be required to adapt the theoretical analysis to these various extensions.

% ----------------------------------------------------------------------------
\paragraph{Conclusion about \textbf{Chapter \ref{chapter:6}}}

@@

% ----------------------------------------------------------------------------
% \paragraph{Perspectives about \textbf{Chapter \ref{chapter:1}}}

% ----------------------------------------------------------------------------
% \paragraph{Perspectives about }}

@@

% ----------------------------------------------------------------------------
% \paragraph{Perspectives about \textbf{Chapter \ref{chapter:3}}}

@@

% ----------------------------------------------------------------------------
\paragraph{Perspectives about \textbf{Chapter \ref{chapter:4}}}

@@

% \paragraph{Possible extensions of the first model}

@@

% \paragraph{Extensions of the demonstration}

@@

% \paragraph{Possible extensions for the second model}

@@

% ----------------------------------------------------------------------------
\paragraph{Perspectives about \textbf{Chapter \ref{chapter:5}}}

@@

% ----------------------------------------------------------------------------
\paragraph{Perspectives about \textbf{Chapter \ref{chapter:6}}}

@@

We would also like to study in the future possible extension of our approach to the slowly varying model, as studied in \cite{Besbes14stochastic,Louedec16,WeiSrivastava18Abruptly}, or the rotted bandit model.

Another interesting direction of future work is to study non-stationary distributed multi-player bandits, to unify the models from Chapter~\ref{chapter:5} and \ref{chapter:6}.
A natural extension of the non-stationary model is to consider non-communicating players cooperating in a decentralized way to play the same bandit game, as it was proposed recently in \cite{WeiSrivastava18Distributed}.
%
We could also build on the proof technique used in \cite{WeiSrivastava18Abruptly}, even if we are interested in removing the hypothesis that player $j$ knows its ID $j\in[M]$ before starting to play.
%
A promising direction is to directly try to join our contributions from Chapter~\ref{chapter:5} and \ref{chapter:6}, and propose an efficient algorithm using three parts:
\klUCB{} indexes for arm selection,
\MCTopM{} for orthogonalization (\ie, dealing with collisions),
and \GLRklUCB{} for non-stationarity (\ie, dealing with abrupt changes).

@@

% ----------------------------------------------------------------------------
\paragraph{Other directions of future works}

>>>>

% First chapter begins here
\chapter{General Conclusion and Perspectives}
% \addcontentsline{toc}{chapter}{General Conclusion}
\label{chapter:conclusion}

% \newpage
\paragraph{Abstract.}
%
This last chapter concludes the thesis, first by summarizing the previous chapters, and by giving a general conclusion of the thesis.
%
We highlight what we consider to be the most important directions of future works, as well as some promising directions that were shortly studied during my PhD but not discussed in the manuscript.

\vspace*{10pt}

\minitoc

@@

\newpage

@@

% % ----------------------------------------------------------------------------
% \paragraph{Conclusion about \textbf{Chapter~\ref{chapter:1}}.}

% ----------------------------------------------------------------------------
\paragraph{Conclusion about \textbf{Chapter~\ref{chapter:2}}.}

@@

The first contribution of this manuscript \cite{Besson2018WCNC} concluded this chapter, in Section~\ref{sec:2:chooseYourPreferredBanditAlgorithm}. We tackle the question of how to select a particular bandit algorithm when a practitioner is facing a particular (unknown) bandit problem.
Instead of always choosing a fixed algorithm, or running costly benchmarks before real-world deployment of the chosen algorithm, a third solution can be to select a few candidate algorithms, where at least one is expected to be very efficient for the given problem, and use online algorithm selection to automatically and dynamically decide the best candidate.
We proposed an extension of the Exp4 algorithm for this problem, \Aggr, and illustrate its performance on some bandit problems.

% ----------------------------------------------------------------------------
\paragraph{Conclusion about \textbf{Chapter~\ref{chapter:3}}.}

@@

We detailed how SMPyBandits is implementing arms, problems, algorithms, and use these components to implement a simulation loop, with various visualizations being performed after the simulation.
As far as now, SMPyBandits is restricted to the finite-arm cases, but it supports a wide range of arms distributions.
Different kinds of models are implemented, from stationary single-player to piece-wise stationary multi-player with different collision models.
One of the main quality of the library is that it is quite exhaustive, as all the main families of algorithms covering these different models have been implemented, even very recent algorithms from the literature, I we tried to follow actively the state-of-the-art research, since December $2016$ to June $2019$.
More than $65$ algorithms (or variants) are implemented for the single-player case, $5$ for the experts aggregation problem, about $15$ for the multi-player case, and about $20$ for the piece-wise stationary case.
The entire codebase is fully documented, and the library is using continuous integration to run automated tests on the code after every modifications.
%
When comparing algorithms on a problem, the main performance measure is the regret, but the library also computes, stores and visualizes other measures, such as best-arm selection rate or mean cumulated reward, as well as real time and memory costs.
%
Our library is used to run numerical simulations on Chapters~\ref{chapter:2}~ \ref{chapter:5} and~\ref{chapter:6}, and in other contributions such as our article \cite{Besson2018DoublingTricks}.

% ----------------------------------------------------------------------------
\paragraph{Conclusion about \textbf{Chapter~\ref{chapter:4}}.}

@@

% ----------------------------------------------------------------------------
\paragraph{Conclusion about \textbf{Chapter~\ref{chapter:5}}.}

The second chapter of Part~\ref{part:MABIOT} of this manuscript studied Multi-Player Multi-Arm Bandits models.
%
We present three variants of this model,
with different level of feedback being available to the decentralized players, under which we proposed efficient algorithms.
For the two easiest models --with sensing--, our theoretical contribution improves the state-of-the-art upper bounds on the regret. In the absence of sensing, we also provide some motivation for the practical use of the interesting \Selfish{} heuristic, a simple index policy based on hybrid indices that are directly taking  into account the collision information.
%
We also reviewed various variants of this model, and for some interesting variants we discussed the related literature, which has proved to be very active in the last two years.
For some of these variants, we explained why our approach does not work efficiently without modifications, but we detailed and illustrated how to adapt \MCTopM{} to other settings.
For example, it assumes to know the number of players $M$ before-hand, but we illustrated that previously introduced technique to estimate $M$ can also be applied to our proposal and give satisfactory empirical performances.
% Further works would be required to adapt the theoretical analysis to these various extensions.

% ----------------------------------------------------------------------------
\paragraph{Conclusion about \textbf{Chapter~\ref{chapter:6}}.}

@@

% ----------------------------------------------------------------------------
% \paragraph{Perspectives about \textbf{Chapter~\ref{chapter:1}}.}

% ----------------------------------------------------------------------------
\paragraph{Perspectives about \textbf{Part~\ref{part:Introduction}}.}

% ----------------------------------------------------------------------------
% \paragraph{Perspectives about }.}

@@

% ----------------------------------------------------------------------------
% \paragraph{Perspectives about \textbf{Chapter~\ref{chapter:3}}.}

@@

% ----------------------------------------------------------------------------
\paragraph{Perspectives about \textbf{Chapter~\ref{chapter:4}}.}

@@

% \paragraph{Possible extensions of the first model.}

@@

% \paragraph{Extensions of the demonstration.}

@@

% \paragraph{Possible extensions for the second model.}

@@

% ----------------------------------------------------------------------------
\paragraph{Perspectives about \textbf{Chapter~\ref{chapter:5}}.}

@@

% ----------------------------------------------------------------------------
\paragraph{Perspectives about \textbf{Chapter~\ref{chapter:6}}.}

@@

We would also like to study in the future possible extension of our approach to the slowly varying model, as studied in \cite{Besbes14stochastic,Louedec16,WeiSrivastava18Abruptly}, or the rotting bandit model \cite{Seznec2018}.

Another interesting direction of future work is to study non-stationary distributed multi-player bandits, to unify the models from Chapter~\ref{chapter:5} and~\ref{chapter:6}.
A natural extension of the non-stationary model is to consider non-communicating players cooperating in a decentralized way to play the same bandit game, as it was proposed recently in \cite{WeiSrivastava18Distributed}.
%
We could also build on the proof technique used in \cite{WeiSrivastava18Abruptly}, even if we are interested in removing the hypothesis that player $j$ knows its ID $j\in[M]$ before starting to play.
%
A promising direction is to directly try to join our contributions from Chapter~\ref{chapter:5} and~\ref{chapter:6}, and propose an efficient algorithm using three parts:
\klUCB{} indexes for arm selection,
\MCTopM{} for orthogonalization (\ie, dealing with collisions),
and \GLRklUCB{} for non-stationarity (\ie, dealing with abrupt changes).

@@

% ----------------------------------------------------------------------------
\paragraph{Other directions of future works.}

### 2019-06-06 4-Listofpublications/Listofpublications.tex
Added https://arxiv.org/abs/1811.11043

\section*{International Conferences}
\renewcommand{\labelenumi}{[IC-\arabic{enumi}]}
\begin{etaremune}
\item
  \href{https://hal.inria.fr/hal-02144465/document}{Decentralized Spectrum Learning for IoT Wireless Networks Collision Mitigation}, by \href{https://moychris.wordpress.com/}{C. Moy} \& \textbf{L. Besson},
  \href{https://sites.google.com/view/ISIoT2019/}{ISIoT Workshop} at \href{https://dcoss.org/}{DCOSS}, Santorini, Greece, May 2019,
  \href{https://hal.inria.fr/hal-02144465}{HAL-02144465}.
  \cite{MoyBesson2019}
\item
  \href{https://perso.crans.org/besson/articles/BMBBM__IEEE_WCNC__2019.pdf}{Upper-Confidence
  Bound for Channel Selection in LPWA Networks with Retransmissions},
  by \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi}, \textbf{L. Besson}, J.
  Manco-Vasquez,
  \href{https://moychris.wordpress.com/}{C. Moy}.
  \href{https://sites.google.com/view/wcncworkshop-motion2019/}{MoTION Workshop} at
  \href{http://wcnc2019.ieee-wcnc.org/}{IEEE WCNC},
  Marrakech, Maroc, April 2019, \href{https://hal.inria.fr/hal-02049824}{HAL-02049824}.
  \cite{Bonnefoi2019WCNC}
\item
  \href{https://perso.crans.org/besson/articles/BBM__Demo_ICT_2018.pdf}{MALIN:
  « Multi-Arm bandit Learning for Iot Networks » with GRC: A TestBed
  Implementation and Demonstration that Learning Helps}, by \textbf{L.
  Besson}, \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi},
  \href{https://moychris.wordpress.com/}{C. Moy}. Demonstration
  presented at ICT (\emph{International Conference on Communication}),
  Saint-Malo, France, June 2018. Cf. \texttt{YouTu.be/HospLNQhcMk}, \href{https://hal.inria.fr/hal-02013866}{HAL-02013866}.
  \cite{Besson2018ICT}
\end{etaremune}

\section*{International Conferences}
\renewcommand{\labelenumi}{[IC-\arabic{enumi}]}
\begin{etaremune}
\item
  \href{https://perso.crans.org/besson/articles/BBM__IEEE_WCNC_2019.pdf}{GNU
  Radio Implementation of MALIN: « Multi-Armed bandits Learning for
  Internet-of-things Networks »}, by \textbf{L. Besson},
  \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi},
  \href{https://moychris.wordpress.com/}{C. Moy}.
  \href{http://wcnc2019.ieee-wcnc.org/}{IEEE WCNC},
  Marrakech, Maroc, April 2019, \href{https://hal.inria.fr/hal-02006825}{HAL-02006825}.
  \cite{Besson2019WCNC}
\item
  \href{https://hal.inria.fr/hal-01629733/document}{Multi-Player Bandits
  Revisited}, by \textbf{L. Besson} \&
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann}.
  \href{http://www.cs.cornell.edu/conferences/alt2018/accepted.html}{ALT}
  (\emph{Algorithmic Learning Theory}), Lanzarote, Spain, April 2018,
  \href{https://hal.inria.fr/hal-01629733}{HAL-01629733}.
  \cite{Besson2018ALT}
\item
  \href{https://hal.inria.fr/hal-01705292/document}{Aggregation of
  Multi-Armed Bandits learning algorithms for Opportunistic Spectrum
  Access}, by \textbf{L. Besson},
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann} \& \href{https://moychris.wordpress.com/}{C. Moy}.
  \href{http://wcnc2018.ieee-wcnc.org/}{IEEE WCNC}, Barcelone, Spain,
  avril 2018, \href{https://hal.inria.fr/hal-01705292}{HAL-01705292}.
  \cite{Besson2018WCNC}
\item
  \href{https://hal.inria.fr/hal-01575419/document}{Multi-Armed Bandit
  Learning in IoT Networks and non-stationary settings}, by
  \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi}, \textbf{L.
  Besson}, \href{https://moychris.wordpress.com/}{C. Moy},
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann} \& J. Palicot. \href{http://crowncom.org/2017/}{CrownCom}
  (\emph{Conference on Cognitive Radio Oriented Wireless Networks}),
  Lisbonne, Portugal, September 2017,
  \href{https://hal.inria.fr/hal-01575419}{HAL-01575419}, \textbf{Best Paper Award}.
  \cite{Bonnefoi17}
\end{etaremune}

\section*{National Conferences}
\renewcommand{\labelenumi}{[NC-\arabic{enumi}]}
\begin{etaremune}
\item
  \href{https://hal.inria.fr/hal-02006471/document}{Analyse non asymptotique d'un test séquentiel de détection de ruptures et application aux bandits non stationnaires}, by \textbf{L. Besson} \&
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann}.
  GRETSI, Lille, August 2019,
  \href{https://hal.inria.fr/hal-02006471}{HAL-02006471}.
  \cite{Besson2019Gretsi}
\end{etaremune}

@@

\section*{Other Publications}
\renewcommand{\labelenumi}{[OP-\arabic{enumi}]}
\begin{etaremune}
\item
  \href{https://hal.inria.fr/hal-02006471/document}{The Generalized Likelihood Ratio Test meets klUCB: an Improved Algorithm for Piece-Wise Non-Stationary Bandits}, by \textbf{L. Besson} \&
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann}, February 2019,
  \href{https://hal.inria.fr/hal-02006471}{HAL-02006471}.
  \cite{Besson2019GLRT}
\item
  \href{https://hal.inria.fr/hal-01840022/document}{SMPyBandits: an
  Open-Source Research Framework for Single and Multi-Players Multi-Arms
  Bandits (MAB) Algorithms in Python}, by \textbf{L. Besson},
  active development since 2016,
  \href{https://hal.inria.fr/hal-01840022}{HAL-01840022}. Code on
  \href{https://GitHub.com/SMPyBandits/SMPyBandits}{GitHub.com/SMPyBandits}
  (about 40000 lines), documentation and tutorials on
  \href{https://SMPyBandits.rtfd.io}{SMPyBandits.rtfd.io}.
  \cite{SMPyBandits,SMPyBanditsJMLR}
\item
  \href{https://hal.inria.fr/hal-01736357/document}{What Doubling-Trick
  Can and Can't Do for Multi-Armed Bandits}, by \textbf{L. Besson} \&
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann}, September 2018,
  \href{https://hal.inria.fr/hal-01736357}{HAL-01736357}.
  \cite{Besson2018DoublingTricks}
\item
  \href{https://hal.inria.fr/hal-01847480/document}{A Note on the Ei
  Function and a Useful Sum-Inequality}, by \textbf{L. Besson}, February
  2018 \href{https://hal.inria.fr/hal-01847480}{HAL-01847480}.
\end{etaremune}

>>>>

\section*{International Workshops}
\renewcommand{\labelenumi}{[IW-\arabic{enumi}]}
\begin{etaremune}
\item
  \href{https://hal.inria.fr/hal-02144465/document}{Decentralized Spectrum Learning for IoT Wireless Networks Collision Mitigation}, by \href{https://moychris.wordpress.com/}{C. Moy} \& \textbf{L. Besson},
  \href{https://sites.google.com/view/ISIoT2019/}{ISIoT Workshop} at \href{https://dcoss.org/}{DCOSS}, Santorini, Greece, May 2019,
  \href{https://hal.inria.fr/hal-02144465}{HAL-02144465},
  \href{https://arxiv.org/abs/1906.00614}{arxiv:1906.00614}.
  \cite{MoyBesson2019}
\item
  \href{https://perso.crans.org/besson/articles/BMBBM__IEEE_WCNC__2019.pdf}{Upper-Confidence
  Bound for Channel Selection in LPWA Networks with Retransmissions},
  by \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi}, \textbf{L. Besson}, J.
  Manco-Vasquez,
  \href{https://moychris.wordpress.com/}{C. Moy}.
  \href{https://sites.google.com/view/wcncworkshop-motion2019/}{MoTION Workshop} at
  \href{http://wcnc2019.ieee-wcnc.org/}{IEEE WCNC},
  Marrakech, Maroc, April 2019,
  \href{https://hal.inria.fr/hal-02049824}{HAL-02049824},
  \href{https://arxiv.org/abs/1902.10615}{arxiv:1902.10615}.
  \cite{Bonnefoi2019WCNC}
\end{etaremune}

\section*{Demonstrations at International Conferences}
\renewcommand{\labelenumi}{[DEMO-\arabic{enumi}]}
\begin{etaremune}
\item
  \href{https://perso.crans.org/besson/articles/BBM__Demo_ICT_2018.pdf}{MALIN:
  « Multi-Arm bandit Learning for Iot Networks » with GRC: A TestBed
  Implementation and Demonstration that Learning Helps}, by \textbf{L.
  Besson}, \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi},
  \href{https://moychris.wordpress.com/}{C. Moy}. Demonstration
  presented at ICT (\emph{International Conference on Communication}),
  Saint-Malo, France, June 2018. Cf. \texttt{YouTu.be/HospLNQhcMk}, \href{https://hal.inria.fr/hal-02013866}{HAL-02013866}.
  \cite{Besson2018ICT}
\end{etaremune}

\section*{International Conferences}
\renewcommand{\labelenumi}{[IC-\arabic{enumi}]}
\begin{etaremune}
\item
  \href{https://perso.crans.org/besson/articles/BBM__IEEE_WCNC_2019.pdf}{GNU
  Radio Implementation of MALIN: « Multi-Armed bandits Learning for
  Internet-of-things Networks »}, by \textbf{L. Besson},
  \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi},
  \href{https://moychris.wordpress.com/}{C. Moy}.
  \href{http://wcnc2019.ieee-wcnc.org/}{IEEE WCNC},
  Marrakech, Maroc, April 2019,
  \href{https://hal.inria.fr/hal-02006825}{HAL-02006825},
  \href{https://arxiv.org/abs/1902.01734}{arxiv:1902.01734}.
  \cite{Besson2019WCNC}
\item
  \href{https://hal.inria.fr/hal-01629733/document}{Multi-Player Bandits
  Revisited}, by \textbf{L. Besson} \&
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann}.
  \href{http://www.cs.cornell.edu/conferences/alt2018/accepted.html}{ALT}
  (\emph{Algorithmic Learning Theory}), Lanzarote, Spain, April 2018,
  \href{https://hal.inria.fr/hal-01629733}{HAL-01629733},
  \href{https://arxiv.org/abs/1711.02317}{arxiv:1711.02317}.
  \cite{Besson2018ALT}
\item
  \href{https://hal.inria.fr/hal-01705292/document}{Aggregation of
  Multi-Armed Bandits learning algorithms for Opportunistic Spectrum
  Access}, by \textbf{L. Besson},
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann} \& \href{https://moychris.wordpress.com/}{C. Moy}.
  \href{http://wcnc2018.ieee-wcnc.org/}{IEEE WCNC}, Barcelone, Spain,
  avril 2018, \href{https://hal.inria.fr/hal-01705292}{HAL-01705292}.
  \cite{Besson2018WCNC}
\item
  \href{https://hal.inria.fr/hal-01575419/document}{Multi-Armed Bandit
  Learning in IoT Networks and non-stationary settings}, by
  \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi}, \textbf{L.
  Besson}, \href{https://moychris.wordpress.com/}{C. Moy},
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann} \& J. Palicot. \href{http://crowncom.org/2017/}{CrownCom}
  (\emph{Conference on Cognitive Radio Oriented Wireless Networks}),
  Lisbonne, Portugal, September 2017,
  \href{https://hal.inria.fr/hal-01575419}{HAL-01575419},
  \href{https://arxiv.org/abs/1807.00491}{arxiv:1807.00491},
  \textbf{Best Paper Award}.
  \cite{Bonnefoi17}
\end{etaremune}

\section*{National Conferences (\emph{in French})}
\renewcommand{\labelenumi}{[NC-\arabic{enumi}]}
\begin{etaremune}
\item
  \href{https://hal.inria.fr/hal-02006471/document}{Analyse non asymptotique d'un test séquentiel de détection de ruptures et application aux bandits non stationnaires}, by \textbf{L. Besson} \&
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann}.
  GRETSI, Lille, August 2019,
  \href{https://hal.inria.fr/hal-02006471}{HAL-02006471}.
  \cite{Besson2019Gretsi}
\end{etaremune}

@@

\section*{Other Publications}
\renewcommand{\labelenumi}{[OP-\arabic{enumi}]}
\begin{etaremune}
\item
  \href{https://hal.inria.fr/hal-02006471/document}{The Generalized Likelihood Ratio Test meets klUCB: an Improved Algorithm for Piece-Wise Non-Stationary Bandits}, by \textbf{L. Besson} \&
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann}, February 2019,
  \href{https://hal.inria.fr/hal-02006471}{HAL-02006471},
  \href{https://arxiv.org/abs/1902.01575}{arxiv:1902.01575}.
  \cite{Besson2019GLRT}
\item
  \href{https://hal.inria.fr/hal-01840022/document}{SMPyBandits: an
  Open-Source Research Framework for Single and Multi-Players Multi-Arms
  Bandits (MAB) Algorithms in Python}, by \textbf{L. Besson},
  active development since 2016,
  \href{https://hal.inria.fr/hal-01840022}{HAL-01840022}. Code on
  \href{https://GitHub.com/SMPyBandits/SMPyBandits}{GitHub.com/SMPyBandits}
  (about 40000 lines), documentation and tutorials on
  \href{https://SMPyBandits.rtfd.io}{SMPyBandits.rtfd.io}.
  \cite{SMPyBandits,SMPyBanditsJMLR}
\item
  \href{https://hal.inria.fr/hal-01736357/document}{What Doubling-Trick
  Can and Can't Do for Multi-Armed Bandits}, by \textbf{L. Besson} \&
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann}, September 2018,
  \href{https://hal.inria.fr/hal-01736357}{HAL-01736357},
  \href{https://arxiv.org/abs/1803.06971}{arxiv:1803.06971}.
  \cite{Besson2018DoublingTricks}
\item
  \href{https://hal.inria.fr/hal-01847480/document}{A Note on the Ei
  Function and a Useful Sum-Inequality}, by \textbf{L. Besson}, February
  2018 \href{https://hal.inria.fr/hal-01847480}{HAL-01847480}.
\end{etaremune}
